Multispecies survey for diet comp

### 2020-12-04 SurveyDietCompTest.Rmd
sum unid prey

  # associate prey with prey category
  # randomly assign up to unidprey % of prey in each prey category to associated unid category

@@

  dat2 <- left_join(dat2, fgsprey) %>%
    group_by(species, time.days, agecl, prey) %>%
    mutate(unidprop = runif(1, 0, unidprey*atoutput))

@@

>>>>

  # associate prey with prey category
  # randomly assign up to unidprey % of prey in each prey category to associated unid category
  # take remainder for identified prey

@@

  dat3 <- left_join(dat2, fgsprey) %>%
    rowwise() %>%
    mutate(unidprop = runif(1, 0, unidprey*atoutput),
           sampprop = atoutput - unidprop)

@@

  unidrows <- dat3 %>%
    #select(-atoutput, -prey, -sampprop) %>%
    group_by(species, time.days, agecl, unidtype) %>%
    summarise(unidtot = sum(unidprop)) %>%
    ungroup() %>%
    rename(prey = unidtype, sampprop = unidtot)
